A Model to Predict Survival in Patients with End-Stage Liver Disease

### 2022-06-06 analysis/article.Rmd
feat: add docx export

author:
    - Sebastian Gibb:
        email: mail@sebastiangibb.de
        institute: [ILM, KAINS]
        correspondence: true
    - Thorsten Kaiser:
        email: thorsten.kaiser@medizin.uni-leipzig.de
        institute: ILM
        correspondence: false
institute:
    - ILM: Institute of Laboratory Medicine, Clinical Chemistry and Molecular Diagnostics, University Hospital Leipzig, Paul-List-Str. 13-15, D-04103 Leipzig, Germany.
    - KAINS: Anesthesiology and Intensive Care Medicine, University Hospital Greifswald, Ferdinand-Sauerbruch-Straße, D-17475 Greifswald, Germany.
date: "`r Sys.Date()`"
bibliography:
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'bibliography.bib')`"
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'rpackages', 'article.bib')`"
output:
  bookdown::html_document2:
    pandoc_args: # pandoc_args doesn't support r evaluation
      - --lua-filter=pandoc/lua-filters/scholarly-metadata.lua
      - --lua-filter=pandoc/lua-filters/author-info-blocks.lua
---

@@

```{r flowchart, results = "asis", echo = FALSE, fig.width = 5, fig.height = 5, fig.cap = "Flowchart Inclusion/Exclusion."}
graph <- "
digraph flowchart {
    graph [splines = false];

>>>>

author:
    - Sebastian Gibb:
        email: mail@sebastiangibb.de
        institute: [ILM, KAINS]
        correspondence: true
    - Thorsten Kaiser:
        email: thorsten.kaiser@medizin.uni-leipzig.de
        institute: ILM
        correspondence: false
institute:
    - ILM: Institute of Laboratory Medicine, Clinical Chemistry and Molecular Diagnostics, University Hospital Leipzig, Paul-List-Str. 13-15, D-04103 Leipzig, Germany.
    - KAINS: Anesthesiology and Intensive Care Medicine, University Hospital Greifswald, Ferdinand-Sauerbruch-Straße, D-17475 Greifswald, Germany.
date: "`r Sys.Date()`"
bibliography:
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'bibliography.bib')`"
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'rpackages', 'article.bib')`"
output:
  bookdown::html_document2:
    pandoc_args: # pandoc_args doesn't support r evaluation
      - --lua-filter=pandoc/lua-filters/scholarly-metadata.lua
      - --lua-filter=pandoc/lua-filters/author-info-blocks.lua
  bookdown::word_document2:
    pandoc_args: # pandoc_args doesn't support r evaluation
      - --lua-filter=pandoc/lua-filters/scholarly-metadata.lua
      - --lua-filter=pandoc/lua-filters/author-info-blocks.lua
---

@@

```{r flowchart, results = "asis", eval = knitr::is_html_output(), echo = FALSE, fig.width = 5, fig.height = 5, fig.cap = "Flowchart Inclusion/Exclusion."}
graph <- "
digraph flowchart {
    graph [splines = false];
